\documentclass[11pt,a4paper]{letter}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

% Increased margins on both sides for a cleaner, centered look
\usepackage[top=1.8cm, bottom=1.5cm, left=2.5cm,  right=2cm, paper=a4paper]{geometry}

\usepackage{microtype, setspace} %% Micro-typographic extensions, linespread
\microtypesetup{final,tracking=true,kerning=true,spacing=true}


\usepackage{hyperref}
\hypersetup{colorlinks,urlcolor=blue}


% --- SENDER INFO ---
\address{
    \textbf{Romain Lafarguette} \\
    36 Chay Yan Street, 169905 Singapore \\
    +65 8710 9760 | \href{mailto:romain.lafarguette@gmail.com}{romain.lafarguette@gmail.com} \\
    \url{https://romainlafarguette.github.io/}
    \vspace{0.5cm}
}

\begin{document}

\begin{letter}{
    ASEAN+3 Macroeconomic Research Office (AMRO) \\
    10 Shenton Way, \#15-08 \\
    MAS Building, Singapore 079117
}


\vspace{0.5cm}
\opening{Dear Members of the AMRO Recruitment Team,}

I am writing to express my strong interest in the Technical Assistance Specialist position at the ASEAN+3 Macroeconomic Research Office (AMRO). My career has been driven by a deep-seated passion for public service and a commitment to strengthening macroeconomic resilience through technical assistance (TA). Having served as a technical assistance specialist at the International Monetary Fund (IMF) and an expert at the European Central Bank (ECB), I am eager to dedicate my expertise to AMRO's vital mandate of securing financial stability across the ASEAN region.\\

My dedication to the public sector is the cornerstone of my professional identity. During my tenure with the IMF, I led or contributed to over 30 technical assistance missions worldwide. This work allowed me to engage directly with authorities in economies such as Vietnam, Malaysia, and the Philippines, where I provided specialized advice on capital controls, sovereign risk, and liquidity management. These experiences instilled in me a deep commitment to building local capacity to ensure long-term regional prosperity.\\

While my recent roles at GIC and ADIA involved deep understanding of global financial markets, I viewed these opportunities as a way to deepen my understanding of global market dynamics within a public-service context. Managing risk and asset allocation for significant sovereign portfolios allowed me to master the complex financial linkages that impact national stability. This market-side experience is a powerful complement to my policy background, providing me with a unique 360-degree view of how global volatility translates into macro-financial risks for member economies.\\

I am particularly aligned with AMRO's goal of fostering regional financial cooperation. My Ph.D. from Peking University, completed entirely in Mandarin, is a testament to my long-standing personal and professional commitment to the region. Throughout my career, I have prioritized the development of practical, open-source decision-support toolkits to empower central bankers with the analytical capabilities they need.\\

I am confident that my multilateral policy experience, combined with my deep technical knowledge of central banking and financial markets, makes me an ideal fit for AMRO. I look forward to the opportunity to contribute to the strategic growth of your technical assistance programs.\\

\closing{Sincerely, Romain Lafarguette, Ph.D.}

\end{letter}
\end{document}